Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-17 tex/paper1/paper1.tex
improved the white-red comparison plot

Figure \ref{fig:comparison} illustrates how a time series generated
from a random sample from a \PL\ \PS\ can be mistakenly thought to
contain a narrow-band oscillatory signal.  The time series (Figure
\ref{fig:comparison}(a)) is constructed from a \PS\ $P(f)\approx
f^{-1.77}$ with no explicit oscillatory content, following the
construction procedure of \cite{2010MNRAS.402..307V}.  {\bf Figure
  \ref{fig:comparison}(b) shows that if the null hypothesis is that
  the time-series is purely noise, and that the noise has the same
  average power at all wavelet scales (for example, if the time-series
  were pure Gaussian noise), then the 95\% confidence level leads to
  the positive detection of significant oscillatory power in this time
  series.}  {\bf The detection claim changes if a different null
  hypothesis is used. Figure \ref{fig:comparison}(d) is the same as
  Figure \ref{fig:comparison}(b) except with the null hypothesis that
  the time-series gives rise to a \PL\ \PS\ of the form
  $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
  oscillation, and $n$ is its power law index}.{\bf The model used to
  generate a \PL\ \PS\ is an auto-regressive AR(1) model.  Such
  time-series assume that the current value in a time-series depends
  on its previous value plus some Gaussian-distributed noise
  \citep{chatfieldtimeseries}.  The null hypothesis that generates the
  \PL\ \PS\ is not important in order to illustrate its effect on the
  detection claim.}  This null hypothesis assumption, with the same
confidence level, significantly reduces the area in the wavelet
transform for which a detection may be claimed.  Even with this
significantly different background assumption, there is still a
significant amount of wavelet power above the 95\% confidence level.
However, since the data is simulated without an explicit oscillatory
component, the high wavelet power must have arisen by chance.  The
simulated data, along with the results of Section \ref{sec:anal},
suggest that when examining the wavelet transforms of time-series for
wave packets, a background \PL\ \PS\ should be assumed, along with
higher confidence levels (99\% or higher), in order to minimize the
effects of mistakenly identifying random variations in the background
\PS\ as evidence for an oscillatory signal.

>>>>

Figure \ref{fig:comparison} illustrates how a time series generated
from a random sample from a \PL\ \PS\ can be mistakenly thought to
contain a narrow-band oscillatory signal.  The time series (Figure
\ref{fig:comparison}(a)) is constructed from a \PS\ $P(f)\approx
f^{-1.77}$ with no explicit oscillatory content, following the
construction procedure of \cite{2010MNRAS.402..307V}.  {\bf Figure
  \ref{fig:comparison}(b) shows that if the null hypothesis is that
  the time-series is purely noise, and that the noise has the same
  average power at all wavelet scales (for example, if the time-series
  were pure Gaussian noise), then the 95\% confidence level leads to
  the positive detection of significant oscillatory power in this time
  series.}  {\bf The detection claim changes if a different null
  hypothesis is used. Figure \ref{fig:comparison}(d) is the same as
  Figure \ref{fig:comparison}(b) except with the null hypothesis that
  the time-series gives rise to a \PL\ \PS\ of the form
  $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
  oscillation, and $n$ is its power law index}\footnote{{\bf The model used to
  generate a \PL\ \PS\ is an auto-regressive AR(1) model.  Such
  time-series assume that the current value in a time-series depends
  on its previous value plus some Gaussian-distributed noise
  \citep{chatfieldtimeseries}.  The null hypothesis that generates the
  \PL\ \PS\ is not important in order to illustrate its effect on the
  detection claim.}}.  This null hypothesis assumption, with the same
confidence level, significantly reduces the area in the wavelet
transform for which a detection may be claimed.  Even with this
significantly different background assumption, there is still a
significant amount of wavelet power above the 95\% confidence level.
However, since the data is simulated without an explicit oscillatory
component, the high wavelet power must have arisen by chance.  The
simulated data, along with the results of Section \ref{sec:anal},
suggest that when examining the wavelet transforms of time-series for
wave packets, a background \PL\ \PS\ should be assumed, along with
higher confidence levels (99\% or higher), in order to minimize the
effects of mistakenly identifying random variations in the background
\PS\ as evidence for an oscillatory signal.
